Modal Abstractions for Virtualizing Memory Addresses

### 2024-11-12 appendix.tex
appendix of c code

\begin{lstlisting}[style=CStyle]
void pte_initialize(pte_t *entry) {

@@

>>>>

\begin{lstlisting}[caption={Page-Table-Entry Library for Page-Table Traversal},label={cpagetablewalk},style=CStyle]
void pte_initialize(pte_t *entry) {

@@

\subsection{Mapping a Page}
\label{sec:cmapapage}

\begin{lstlisting}[caption={Mapping a Single Page},label={cmapapage},style=CStyle]
complstatus_t vaspace_mappage(
    pte_t *pml4,
    void *va,
    uintptr_t pa,
    uint64_t perm
) {
    char *a;
    pte_t *pte;

    a = (char *)PGROUNDUP((uintptr_t)va);

    pte = walkpgdir_succ(pml4, a);
    if (!pte->present){
      pte->writable     = PTE_WRITEABLE_SET(perm);
      pte->user_acc     = PTE_USER_ACC_SET(perm);
      pte->writethrough = PTE_WRITETHRU_SET(perm);
      pte->nocache      = PTE_NOCACHE_SET(perm);
      pte->pfn          = PTE_ADDR_TO_PFN(pa);
      pte->nx           = PTE_NX_SET(perm);
      pte->present      = 1;
    }

    return COMPL_SUCCESS;
}
\end{lstlisting}

\subsection{Address-Space-Switch}
\label{sec:caspaceswitch}

\begin{lstlisting}[caption={Loading \textsf{cr3} for Address-Space Switch},label={caspace},style=CStyle]
void pte_load(pte_t *pml4) {
    lcr3(V2P(pml4));
}
\end{lstlisting}
